Lightweight Ruby Framework for Improving Embedded Software Efficiency

### 2016-08-16 CPSNA2016/short_paper.tex
add short_paper

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems applied to Cyber Physical Systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., a lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improve development efficiency more than the current version.
In the proposed framework, a Bluetooth loader which receives an mruby bytecode, and a RiteVM scheduler which simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
% Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

@@

\section{Introduction}
Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
Embedded systems are applied to the CPS and expected to demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in the large source code, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.
%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
Moreover, Ruby is often utilized in network programming, therefore mruby on TECS can be applicable for the software involved network such as CPS applications.

However, it is not particularly efficient, at present, and imposes a heavy burden on developers.
mruby on TECS only supports a storage/ROM device for loading mruby programs.
Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
In addition, although mruby on TECS can support multi-VM, executing multiple tasks requires the developers to call the OS function.

@@

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD.}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

{\bf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the bytecode after the development phase should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
The proposed loader newly supports a load for bytecodes of scripting languages.

@@

First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); line 4 in Figure \ref{maincode_mrubybluetooth}).
The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
This process is exclusively carried out by the semaphore to prevent the other loading from interrupting.

@@

Finally, the RiteVM runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
When an mruby application is modified, only the bytecode of the application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
% The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
% When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
The proposed framework supports continuous loading; thus, this process loops.
After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
In addition, the proposed framework supports the reset component which force applications stop and free, thus developers can transfer new bytecodes and run tasks.

@@

\subsubsection{RiteVM Scheduler Design}
Here, assumed that two tasks with equal priority are in an infinite loop.
 In the current system, when one task is executed first, the other task would not be executed because the first task runs in the loop.

@@

We evaluated to demonstrate that a Bluetooth loader can improve the efficiency of software development, that the proposed multitask processing executes effectively compared to existing multitask processing or co-routine, and that the initiation of mruby applications are synchronized.
In addition, we focused on benefits of CBD.
We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.

{\bf Improving Development Efficiency by Bluetooth Loader.}
The Bluetooth loader can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

%\subsubsection{Size and time for transferred mruby bytecodes}
In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
To confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
Loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
Similarly, the overhead to compile a zero byte program is 46.9 msec.
The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
The difference increases as the number of RiteVMs increases because 50 msec of overhead is incurred per RiteVM. 
These advantages improve the efficiency of software development.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

{\bf Synchronization of Multiple RiteVM Tasks.}
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.

{\bf Benefits of Component-Based Development.}
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

@@

\clearpage
\appendices
\section{mruby}
\label{apn:mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[b]
    \centering
    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-3mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-3mm}
    \label{fig:mruby}
\end{figure}

\section{TECS}
\label{apn:TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

In TECS, component deployment and composition are performed statically.
Consequently, connecting components does not incur significant overhead and memory requirements can be reduced.
TECS can be implemented in C, and demonstrates various feature such as source level portability and fine-grained components.

\begin{figure}[b]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-5mm}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and variables of a {\it cell}.

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

% \begin{description}
    %\item[
    {\bf Signature Description:\ }%]\mbox{}\\
        {\it Signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.

    %\item[
    {\bf Celltype Description:\ }%]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.

    %\item[
    {\bf Build Description:\ }%]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[H]
\centering
\begin{lstlisting}
signature sMotor {
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Signature Description}
    \vspace{-5mm}
\label{signature}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr { int32_t port; };
    var { int32_t currentSpeed = 0; };
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Celltype Description}
    \vspace{-5mm}
\label{celltype}
\end{figure}

\begin{figure}[H]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}
% \section{mruby on TECS}
% \subsection{System Model}
% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% TECS components support various embedded drivers such as motor and sensor drivers.
%
% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
%     \vspace{-2mm}
% \caption{System model of existing mruby on TECS}
%     \vspace{-2mm}
% \label{fig:mrubyontecs}
% \end{figure}
%
% \subsection{mruby-TECS Bridge}
% There is a significant difference between the execution times of mruby and C language codes.
% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% Thus, it is difficult to use mruby exclusively.
%
% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
%
% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% The left side of BridgeMotor belongs to the mruby program.
% The right side of BridgeMotor belongs to TECS component.
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
%     \vspace{-2mm}
% \caption{mruby-TECS bridge}
%     \vspace{-2mm}
% \label{fig:mruby_TECS_bridge}
% \end{figure}
%
% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
%
% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
%
\end{document}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems applied to Cyber physical systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs scripting language (i.e., a lightweight Ruby) and supports component-based development, has been proposed.
This paper proposes an extended framework of mruby on TECS that improves development efficiency more than the current version.
In the proposed framework, a Bluetooth loader that receives an mruby bytecode, and a RiteVM scheduler that simplifies multitasking are implemented.
% In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
% Moreover, while the framework supports multiple virtual machines, developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
% To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
% The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
% The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
% In addition, multiple mruby programs can run cooperatively in the proposed framework.
% Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
% Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
% Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

@@

\section{Introduction}
Cyber Physical Systems (CPS) are important keywords for enriching our lives.
Embedded systems are applied to the CPS and are expected to demonstrate high quality and performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

In addition, scripting languages, such as Ruby, JavaScript, Perl, Python, and Lua, offer efficient approaches to software development.
Currently, most software are programmed in C language.
However, development in C language results in a large source code, incurs high costs, and requires significant development time.
In contrast, the use of scripting languages improves the efficiency of software engineering and can shorten the development period because of their usability. 
% script languages have high-productivity from their usability.
% Ruby, JavaScript, Perl, Python, and Lua are well-known as representative script languages.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.
%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
The execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of the C language.
Moreover, Ruby is often used in network programming; therefore, mruby on TECS can be applicable for the software involved networks such as CPS applications.

However, at present, mruby on TECS is not particularly efficient, and imposes a heavy burden on developers.
mruby on TECS only supports a storage/ROM device for loading mruby programs.
Consequently, if mruby programs are modified, an SD card must be inserted and removed repeatedly or the ROM must be rewritten; moreover, developers need to restart an RTOS on the target device.
In addition, although mruby on TECS can support multi-VM, executing multiple tasks requires the developers to call the OS function.

@@

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
    % \vspace{-2mm}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
% The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples (a Bluetooth loader, a sheduler, and Eventflags).
    % \vspace{-2mm}
\end{enumerate}

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model, and Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extension of mruby on TECS \cite{par:mrubyonTECS}, and utilizes mruby and TECS, which are also described in \cite{par:mrubyonTECS}.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the bytecode after the development phase should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} can support a load of object files.
The proposed loader newly supports a load for bytecodes of scripting languages.

@@

First, the Bluetooth loader receives the mruby application bytecode from the host (Figure \ref{fig:control_flow}(A); line 4 in Figure \ref{maincode_mrubybluetooth}).
The bytecode is stored in a component variable, such as {\it VAR\_irepApp}, as shown in Figure \ref{celltype_mrubybluetooth}.
This process is exclusively carried out by the semaphore in order to prevent the other loading from interrupting.

@@

Finally, the RiteVM runs (Figure \ref{fig:control_flow}(E); line 14 in Figure \ref{maincode_mrubybluetooth}).
When an mruby application is modified, only the bytecode of the application should be transferred; the mruby libraries do not need to be touched because they typically do not change.
% The process shown in Figure \ref{maincode_mrubybluetooth} (lines 23-28) is carried out when an exception occurs.
% When all mruby applications are completed, mrb\_state and mrbc\_context are freed (lines of 31-34 in Figure \ref{maincode_mrubybluetooth}).
The proposed framework supports continuous loading; thus, this process loops.
After the variables are freed (lines 17, 19 in Figure \ref{maincode_mrubybluetooth}), the RiteVM waits for the next mruby application bytecode.
In addition, the proposed framework supports the reset component that forces applications to stop and free; enabling developers to transfer new bytecodes and run tasks.

@@

\subsubsection{RiteVM Scheduler Design}
Here, assume that two tasks with equal priority are in an infinite loop.
In the current system, when one task is executed, the other task does not get executed because the first task runs in a loop.

@@

We demonstrated that a Bluetooth loader can improve the efficiency of software development and that the proposed multitask processing executes effectively compared with existing multitask processing or co-routine.
In addition, the initiation of mruby applications is synchronized.
Moreover, we focused on the benefits of CBD.
We implemented the proposed system on a LEGO MINDSTORMS EV3 \cite{par:EV3} (300MHz ARM9-based Sitara AM1808 system-on-a-chip) compiled with gcc 4.9.3 -O2 and mruby version 1.2.0.

{\bf Improving Development Efficiency by Bluetooth Loader:}
The Bluetooth loader can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.

%\subsubsection{Size and time for transferred mruby bytecodes}
In the proposed framework, to further improve software development efficiency, developers transfer only the mruby application bytecode; mruby libraries are incorporated in the platform.
In order to confirm the advantage of the proposed design, we evaluated the size, loading time, and compile time between an mruby application with and without mruby library are shown in Table \ref{tab:size_and_time}.
The loading Time indicates how long it takes to process a transferred bytecode in the loader, and the overhead of loading a zero byte bytecode is 50.933 msec.
Similarly, the overhead to compile a zero byte program is 46.9 msec.
The mruby application bytecode is smaller and faster than including the mruby libraries for all terms.
The difference increases as the number of RiteVMs increases because 50 msec of overhead is incurred per RiteVM. 
These advantages improve the efficiency of software development.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slowdown compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spreads the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

{\bf Synchronization of Multiple RiteVM Tasks:}
To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within (periodic time)$\times$(number of RiteVM tasks $-$ 1).
Figure \ref{fig:eval_synchronization} shows the results for two, three, and four RiteVM tasks.
% Figure \ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
The periodic time is 1 msec, and the number of RiteVMs is two, three, and four.
As shown in Figure \ref{fig:eval_synchronization}, the time is within 1 msec, 2 msec, and 3 msec respectively, which indicates successful synchronization of multiple RiteVM tasks.

{\bf Benefits of Component-Based Development:}
In the proposed framework, RiteVMs, the RiteVM scheduler, and Eventflags are implemented as TECS components.
Developers can add or remove the functionalities easily by modifying the CDL file.
Moreover, CBD decreases code size and improves productivity and maintainability.

@@

% \clearpage
% \appendices
% \section{mruby}
% \label{apn:mruby}
% Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
% \begin{figure}[b]
%     \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
%     \vspace{-3mm}
%     \vspace{-3mm}
% \section{TECS}
% \label{apn:TECS}
% \begin{figure}[b]
%     \vspace{-2mm}
%     \vspace{-5mm}
% % \begin{description}
%     %\item[
%     {\bf Signature Description:\ }%]\mbox{}\\
%         {\it Signature} defines a {\it cell} interface.
%     %\item[
%     {\bf Celltype Description:\ }%]\mbox{}\\
%     %\item[
%     {\bf Build Description:\ }%]\mbox{}\\
% % \end{description} 
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-5mm}
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-5mm}
% \begin{figure}[H]
%     \vspace{-2mm}
%     \vspace{-2mm}
% % \section{mruby on TECS}
% % \subsection{System Model}
% % The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% % Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% % TECS components support various embedded drivers such as motor and sensor drivers.
% %
% % An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% % The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% % mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
% %
% % \begin{figure}[t]
% %     \centering
% %     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
% %     \vspace{-2mm}
% % \caption{System model of existing mruby on TECS}
% %     \vspace{-2mm}
% % \label{fig:mrubyontecs}
% % \end{figure}
% %
% % \subsection{mruby-TECS Bridge}
% % There is a significant difference between the execution times of mruby and C language codes.
% % According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% % Thus, it is difficult to use mruby exclusively.
% %
% % Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% % However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
% %
% % Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% % The left side of BridgeMotor belongs to the mruby program.
% % The right side of BridgeMotor belongs to TECS component.
% % \begin{figure}[t]
% %     \centering
% %     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
% %     \vspace{-2mm}
% % \caption{mruby-TECS bridge}
% %     \vspace{-2mm}
% % \label{fig:mruby_TECS_bridge}
% % \end{figure}
% %
% % The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
% %
% % The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% % Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% % Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
% %
\end{document}
